Selective stock enhancement undermines community stability

### 2022-01-25 rmd/supporting_info.Rmd
Update supporting_info.Rmd

```{=tex}
\begin{equation}
\begin{aligned}
  y_j &\sim Normal(\mu_j, \sigma^2)\\
  \mu_j &= \psi_0 + \psi_1~R_j
\end{aligned}
\end{equation}
```

where $\psi_k$ ($k = 0-1$) are the intercept ($\psi_0$) and regression coefficient ($\psi_1$). We extracted 500 estimates of $\psi_1$, each of which represents the effect of stock enhancement $R$ on community dynamics under a given parameter combination. To examine influences of simulation parameters (**Table S1**) on $\psi_1$, we developed the following regression model taking $\psi_1$ as a response variable (parameter combination $n$):

```{=tex}
\begin{equation}
\begin{aligned}
  \psi_{n} &\sim Normal(\mu_n, \sigma^2)\\
  \mu_n &= \zeta_0 + \zeta_1 S_n + \zeta_2 K_n + \zeta_3 r_{1,n} + \zeta_4 r_{max,n} + \zeta_5 \sigma_{\epsilon,n} + \zeta_6 f_{R, n} + \zeta_7 \bar{\alpha}_n
\end{aligned}
\end{equation}
```

@@

@@

# Table S6-8
## load regression tables
source(here::here("code/table_reg.R"))
j <- 5

>>>>

```{=tex}
\begin{equation}
\begin{aligned}
  y_j &\sim Normal(\mu_j, \sigma^2)\\
  \mu_j &= \xi_0 + \xi_1~R_j
\end{aligned}
\end{equation}
```

where $\xi_k$ ($k = 0-1$) are the intercept ($\xi_0$) and regression coefficient ($\xi_1$). We extracted 500 estimates of $\xi_1$, each of which represents the effect of stock enhancement $R$ on community dynamics under a given parameter combination. To examine influences of simulation parameters (**Table S1**) on $\xi_1$, we developed the following regression model taking $\xi_1$ as a response variable (parameter combination $n$):

```{=tex}
\begin{equation}
\begin{aligned}
  \xi_{1,n} &\sim Normal(\mu_n, \sigma^2)\\
  \mu_n &= \zeta_0 + \zeta_1 S_n + \zeta_2 K_n + \zeta_3 r_{1,n} + \zeta_4 r_{max,n} + \zeta_5 \sigma_{\epsilon,n} + \zeta_6 f_{R, n} + \zeta_7 \bar{\alpha}_n
\end{aligned}
\end{equation}
```

@@

## Table S6 Priors
Prior distributions used in the Bayesian models.

```{r table_s6}

# Table S6
source(here::here("code/table_prior.R"))

kable(df_prior, format = "markdown")

@@

# Table S7-9
## load regression tables
source(here::here("code/table_reg.R"))
j <- 6
